The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-24 paper/ms.tex
cleanig the intro

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints between the star formation rate and
dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the luminosity function data
obtained with from CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching methodology using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.
\end{abstract}

\section{Introduction}
\label{sec:intro}
Cosmological simulations still playing an important role on astrophysics and
cosmology. They have become the bridge between observations and theory, a
laboratory where is possible to create universes with different parameters and
new physics.

This is an important tool in the study of dark matter. Since its existence was
purposed, DM has been not observed directly neither on telescopes or high energy
particle colliders, there exists many other theories explaining the observed
universe behavior modifying the gravity itself.

The most successful and accepted cosmological model is the Lambda-CDM. 
Dark matter is a significative component of the universe.
\citep{trimble87}

Hierarchy Structure Evolution: Early formation of small structures
merging on major structures after.

From simulations, Halo Mass Function as function of redshift (or time).

In this paper is established a relation between dark matter and galaxy
luminosity functions at high redshifrt. This relation is a direct
connection between the Lambda-CDM model and the farthest galaxy observations
made with space and grounded telescopes.

Star formation rate as function of time. Peak at $z\sim 2$.

Main Objetive: Reproduce the observed luminosity function at redshift $z=5.9$
from a DMH catalog from simulations.

This paper is organized as follows: In section 2... in section 3...

@@

%  The HMF is created using the DMH catalog from the Multidark Database 
%\citep{riebe13}.

@@

Luminosity Functions (LF) are usually expressed in terms of magnitude instead 
luminosity. Luminosity is the energy emmited by a source in a given wavelengt range, 
is a physical quantity.

Magnitude is a classification inherited from ancient Greeks, this
quantifies the response of the first astrometric device: the human eye, this
perception grows loarithmically with the retrieved radiation.

Luminosity of any object can be compared with Sun Luminosity $(L_{\lambda
\odot})$ at any wavelengt. With the Sun Magnitude as reference
$(M_{\lambda \odot})$, the absolute magnitud of the objet  at an specific
wavelengt is given by: 
 \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$. The solar luminosity can be used as
refference unit, in this fashion, the typical luminosity of a galaxy can be expresed in
terms of $10^{8}-10^{11}$ times the sun luminosity.

>>>>

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the luminosity function data
obtained with from CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching methodology using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.
We also measure the influence on the results of the dust extinction
scaling derived from observations by Bouwens.
We compare our results against the results of abundance matching
methods, a semi-analytic model of galaxy formation (GALFORM) and a
hydrodynamical simulation (Illustris).
\end{abstract}

\section{Introduction}
\label{sec:intro}

@@

@@

L
Luminosity of any object can be compared with Sun Luminosity $(L_{\lambda
\odot})$ at any wavelengt. With the Sun Magnitude as reference
$(M_{\lambda \odot})$, the absolute magnitud of the objet  at an specific
wavelengt is given by: 
 \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$. The solar luminosity can be used as
refference unit, in this fashion, the typical luminosity of a galaxy can be expresed in
terms of $10^{8}-10^{11}$ times the sun luminosity.
